---
title: Analysis
description: 
toc: true
featuredVideo:
featuredImage: 
draft: false
---

We describe here our detailed data analysis.


```{r}
library(tidyverse)
library(ggplot2)
print(getwd())
data <- read_csv(here::here("dataset/income_mortality.RData"))
load(here::here("dataset/income_mortality.RData"))
print(ls())
```

## Note on Attribution

If you are directly quoting from a source, please make that clear. You can show quotes using `>` like this




```
> To be or not to be.
```

> To be or not to be.

Also, make sure to provide a link or citation to where you are quoting from.

-------

## Motivation for Our Data Analysis

Our data is mainly driven by investigating 




## Initial Questions for Data Analysis



## Modeling and Inference

```{r}
nd_regions <- nd[205:215,]

ggplot(nd_regions, aes(Country , LowBirthWT,  fill=Country)) + 
    coord_flip() +
    geom_bar(stat="identity", width=.90) + 
    xlab("Region") + 
    ylab("Low Birth Weight Percentage") + 
    guides(fill=FALSE) +
    ggtitle("Percentage of Children Underweight in World Regions") + 
    theme_minimal()
```
```{r}

load(here::here("dataset/income_mortality.RData"))
#load(here::here("static/load_and_clean_data.R"))
suppressPackageStartupMessages(library(tidyverse))

#maybe need to include different regions and color them with "color = " under ggplot aes (instead of Income)

income_mortality %>% filter(Year == "1950" | Year == "1975" | Year == "2000" | Year == "2020") %>% ggplot(aes(x = Income, y = Mortality, color = Income)) + geom_point(size = 0.3) +
  facet_wrap(~as.factor(Year)) +
  stat_smooth(aes(group = Year), color='black', alpha = 0.4, geom = "line") +
  scale_x_log10() +
  labs(x = "Income Per Capita (PPP)", y = "Under 5 Mortality Rate", title = "Disparity across Under 5 Mortality Rates has decreased over time")
```

## Clarity Figures

  
  
*explain your plots here  

```{r}
# Interesting structure for visualizing mortality rates by world regions when we'll have the world regions variable in the income_mortality data set

 #ggplot(nd_regions, aes(x=Country, y=LowBirthWT, color=Country)) +
     #geom_point(position="jitter") +
     #coord_polar("x") +
     #labs(title="% of Low Birth Weights by World Region", x="", y="", color ="Country" )
```



```{r}
data(income_mortality)
corr <- round(cor(income_mortality$Income), 1)
#not sure how to show the mortality
# Plot
ggcorrplot(corr, hc.order = TRUE, 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           method="circle", 
           colors = c("tomato2", "white", "springgreen3"), 
           title="Correlogram of mortality", 
           ggtheme=theme_bw)

```

