---
title: Model and Inference
description:
toc: true
authors: []
tags: []
categories: []
series: []
date: 2022-12-14T22:00:48-05:00
lastmod: 2022-12-14T22:00:48-05:00
featuredVideo:
featuredImage: 
draft: false
---


```{r echo=FALSE}
suppressPackageStartupMessages(library(ggplot2)) 
#library(olsrr)
suppressPackageStartupMessages(library(hrbrthemes))
suppressPackageStartupMessages(library(GGally))
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyverse))

load(here::here("dataset/income_mortality.RData"))
load(here::here("dataset/nd_regions.RData"))
load(here::here("dataset/nd_inc_mort_avg.RData"))

```



After loading in our combined data set for nutrition, income, and mortality averages, we first created a correlation matrix to see what variables have the highest correlation with Mortality. This helped us view the correlation between all of our variables in this set, and get a better sense as to what kind of model we would like to create, and with what variables. 





### Linear Model 

```{r echo=FALSE, warning = FALSE}
#Scatter Plot and Correlation Matrix of all Variables
model_data <- (select(nd_inc_mort_avg, c(2,4,6,7,10,11,12,13,15,14)))
model_data <- na.omit(model_data)
ggpairs(model_data, upper = list(continuous = wrap("points", alpha = 0.3, size=0.1)),
        lower = list(continuous = wrap('cor', size = 4)))
```




From the correlation matrix we see that those variables are: LowBirthWT, Income_avg, DietDiversity and ZeroVegtable.




```{r echo=FALSE}
model <- lm(model_data$Mortality_avg ~ model_data$LowBirthWT + model_data$DietDiversity + model_data$ZeroVegtable + model_data$MinAcceptDiet + model_data$MinMealFreq)
summary(model)
```





In order to make a more accurate decision, we then ran AIC on the model with these chosen variables. In the end, this resulted in us removing the zero vegetable variable from our model. 

```{r}
step(model, direction = 'both')
```


 

 
