---
title: Model and Inference
description:
toc: true
authors: []
tags: []
categories: []
series: []
date: 2022-12-14T22:00:48-05:00
lastmod: 2022-12-14T22:00:48-05:00
featuredVideo:
featuredImage: 
draft: false
---

```{r echo=FALSE}
suppressPackageStartupMessages(library(ggplot2)) 
#library(olsrr)
suppressPackageStartupMessages(library(hrbrthemes))
suppressPackageStartupMessages(library(GGally))
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyverse))

print(getwd())
load(here::here("dataset/income_mortality.RData"))
load(here::here("dataset/nd_regions.RData"))
load(here::here("dataset/nd_inc_mort_avg.RData"))
print(ls())
```


After loading in our combined data set for nutrition, income, and mortality averages, we first created a correlation matrix. This helped us view the correlation between all of our variables in this set, and get a better sense as to what kind of model we would like to create, and with what variables. 



### Linear Model 

```{r echo=FALSE, warning = FALSE}
#Scatter Plot and Correlation Matrix of all Variables
model_data <- select(nd_inc_mort_avg, c(2,6,7,10,11,12,13,14,15))
ggpairs(model_data, upper = list(continuous = wrap("points", alpha = 0.3, size=0.1)),
        lower = list(continuous = wrap('cor', size = 4)))
```



Based off this, we chose low birthweight, diet diveristy, zero vegetable consumption, minimum acceptable diet, and minimum meal frequency to be the best predictors for our model. 



```{r echo=FALSE, warning = FALSE}
model <- lm(nd_inc_mort_avg$Mortality_avg ~ nd_inc_mort_avg$LowBirthWT + nd_inc_mort_avg$Income_avg + nd_inc_mort_avg$ExclusiveBreastFeeding + nd_inc_mort_avg$DietDiversity + nd_inc_mort_avg$ZeroVegtable)
summary(model)
```


In order to make a more accurate decision, we then ran AIC on the model with these chosen variables. In the end, this resulted in us removing the zero vegetable variable from our model. 



```{r echo=FALSE, warning = FALSE}
ggplot(nd_inc_mort_avg, aes(x=nd_inc_mort_avg$Mortality_avg, y=nd_inc_mort_avg$Income_avg)) + geom_point()
ggplot(nd_inc_mort_avg, aes(x=nd_inc_mort_avg$Mortality_avg, y=nd_inc_mort_avg$DietDiversity)) + geom_point()

model <- glm(nd_inc_mort_avg$Mortality_avg ~ nd_inc_mort_avg$Income_avg + nd_inc_mort_avg$DietDiversity)
summary(model)
```

```{r}
step(model, direction = 'both')
```


 


